Black hole symphony orchestra: Spectroscopy using gravitational wave signals from the inspiral, merger and ringdown of binary black holes

### 2020-11-17 papers/intro_paper/intro_paper.tex
minor update
updated noise systematics figure

First, we demonstrate our method on gravitational wave signals from BBH systems that are well described by GR. We inject simulated GW signals modellng inspiral, merger and ringdown of BBHs  into coloured Gaussian noise described by Advanced LIGO-Virgo design sensitivity in the high-power, zero-detuning configuration (ZDHP) CITE. In particular we choose parameters similar to two specific GW events, GW150914 CITE and GW190521 CITE. The details of the injections are provided in Table~\ref{tab:injection_values}. These two systems are representative data points for the kind of systems this test is most suitable for: high-mass events which are loud enough that the signal-to-noise ratio pre- and post-merger return reliable parameter estimation results. To avoid possible systematic biases in our parameter estimation results due to error in modelling, we use the GR version of the same waveform, $\SEOB$ CITE (without allowing for deviations in the QNM parameters) to simulate our GW signal. And to avoid systematic biases due to noise, we use an averaged (zero-noise) realisation of the Advanced LIGO zero-detuned-high-power PSD CITE. As in the case of the actual detections, we consider a two-detector advanced LIGO network at Hanford and Livingston, having identical PSDs. The distance to the two simulated events is rescaled such that the SNR in the detector network is same as the actual event, i.e, 24 (14) for GW150914 (GW190521). Since (almost) equal-mass binaries like GW150914 and GW190521 observed at moderate high SNRs are not expected to have a loud ringdown signal, we restrict ourselves to estimating the frequency and damping time of the $(\ell m) = (2,2)$, i.e., $\{\df{220},\dtau{220}\}$, while fixing the other QNM frequencies to their GR values.

@@

\appendix
\section{Study of noise syetematics on ringdown measurements}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
	\includegraphics[width=0.4\textwidth]{figures/S190521g_swinjs.png}
	\caption{\textcolor{red}{FINAL RESULT}a single figure for both Gaussian and Real noise injections, color coded, to save space}\label{fig:21g_systematics}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

First, we demonstrate our method on gravitational wave signals from BBH systems that are well described by GR. We inject simulated GW signals modellng inspiral, merger and ringdown of BBHs  into coloured Gaussian noise described by Advanced LIGO-Virgo design sensitivity in the high-power, zero-detuning configuration (ZDHP) CITE. In particular we choose parameters similar to two specific GW events, GW150914 CITE and GW190521 CITE. The details of the injections are provided in Table~\ref{tab:injection_values}. These two systems are representative data points for the kind of systems this test is most suitable for: high-mass events which are loud enough that the signal-to-noise ratio pre- and post-merger return reliable parameter estimation results. To avoid possible systematic biases in our parameter estimation results due to error in modelling, we use the GR version of the same waveform, $\SEOB$ CITE (without allowing for deviations in the QNM parameters) to simulate our GW signal. And to avoid systematic biases due to noise, we use an averaged (zero-noise) realisation of the Advanced LIGO zero-detuned-high-power PSD CITE. A detailed study on noise systematics for one of the GW events is presented in Appendix~\ref{sec:noise_systematics}. As in the case of the actual detections, we consider a two-detector advanced LIGO network at Hanford and Livingston, having identical PSDs. The distance to the two simulated events is rescaled such that the SNR in the detector network is same as the actual event, i.e, 24 (14) for GW150914 (GW190521). Since (almost) equal-mass binaries like GW150914 and GW190521 observed at moderate high SNRs are not expected to have a loud ringdown signal, we restrict ourselves to estimating the frequency and damping time of the $(\ell m) = (2,2)$, i.e., $\{\df{220},\dtau{220}\}$, while fixing the other QNM frequencies to their GR values.

@@

\appendix
\section{Study of noise syetematics on ringdown measurements}\label{sec:noise_systematics}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
	\includegraphics[width=0.4\textwidth]{figures/S190521g_swinjs.png}
	\caption{\textcolor{red}{FINAL RESULT}90 \% credible level on the posterior probability distribution of the frequency and damping time of $(2,\pm 2)$ mode, $(\fgr{220}, \taugr{220}$ from simulations of an \texttt{NRSur7dq4} GW signal with parameters similar to the GW event, GW190521, in Gaussian noise (grey dot-dashed lines) and real interferometric noise (pink dot dashed lines). The GR prediction for the frequency and damping time is indicated by the black cross. While the Gaussian noise simulations are consistent with the prediction, at least 3 or the 5 real noise simulation are not. For comparison, we also plot the 90 \% credible level for the actual event, GW190521.}
	\label{fig:21g_systematics}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
